Nextstrain: real-time tracking of virus evolution

### 2017-10-10 whitepaper.tex
fixed types

\abstract{
\textbf{Summary:}
Understanding the spread and evolution of viral pathogens is important for effective public health measures and surveillance.
%Genomic epidemiology, aided by the often high rates of viral evolution and ability to rapidly disseminate around the world, improves our understanding of such diseases.
Nextstrain consists of a bioinformatics pipeline for phylodynamics analysis of viral genomes and a to an interactive visualisation platform which presents a real-time view into the evolution and spread of a range of viral pathogens of high human importance.
The visualization integrates sequence data with other data types such as geographic information, serology, or host species.
Nextstrain makes these results, representing our current understanding, publicly available for use by health professionals, epidemiologists, virologists and the public alike.
\\
\textbf{Availability and implementation:}
All code (predominantly Javascript and Python) is freely available from https://github.com/nextstrain and the web-application is available at www.nextstrain.org.
\\
\textbf{Contact:}
\href{jhadfiel@fredhutch.org}{jhadfiel@fredhutch.org}, \href{tbedford@fredhutch.org}{tbedford@fredhutch.org}, \href{richard.neher@unibas.ch}{richard.neher@unibas.ch}
\\
}

@@

The regularly updated nature and rapidity of these analyses is crucial to the monitoring and understanding of pathogen epidemiology and evolution.
Sequencing times and costs are continually dropping, with on-the-ground sequencing being employed during the recent West African Ebola and Zika epidemics \citep{quick2016real,faria2017epidemic}.
This rapidity of sequencing must be complemented with rapid methods by which to analyse, interpret, and diseminate results.

>>>>

\abstract{
\textbf{Summary:}
Understanding the spread and evolution of viral pathogens is important for effective public health measures and surveillance.
%Genomic epidemiology, aided by the often high rates of viral evolution and ability to rapidly disseminate around the world, improves our understanding of such diseases.
Nextstrain consists of database, a bioinformatics pipeline for phylodynamics analysis of viral genomes, and an interactive visualisation platform which presents a real-time view into the evolution and spread of a range of viral pathogens of high human importance.
The visualization integrates sequence data with other data types such as geographic information, serology, or host species.
Nextstrain makes these results, representing our current understanding, publicly available for use by health professionals, epidemiologists, virologists and the public alike.
\\
\textbf{Availability and implementation:}
All code (predominantly Javascript and Python) is freely available from https://github.com/nextstrain and the web-application is available at www.nextstrain.org.
\\
\textbf{Contact:}
\href{jhadfiel@fredhutch.org}{jhadfiel@fredhutch.org}, \href{tbedford@fredhutch.org}{tbedford@fredhutch.org}, \href{richard.neher@unibas.ch}{richard.neher@unibas.ch}
\\
}

@@

The regularly updated nature and rapidity of these analyses is crucial to the monitoring and understanding of pathogen epidemiology and evolution.
Sequencing times and costs are continually dropping, with on-the-ground sequencing being employed during the recent West African Ebola and Zika epidemics \citep{quick2016real,faria2017epidemic}.
This rapidity of sequencing must be complemented with rapid methods by which to analyse, interpret, and disseminate results.
